%******************************************************************************************************
\chapter[Introduction]{Quantifying Uncertainty of Computer Model: Forward and Backward}\label{ch:intro}
%******************************************************************************************************

% Introductory Paragraphs
\begin{quote}
	``All models are wrong but some are useful -- George Box''
\end{quote}
It is perhaps convenient to use, at least half of it, the quote by Box as an excuse if a modeling exercise goes awry.
But engineers are constructive bunch, as they are pragmatic, so they often focus on the second part of the statement and try to do better.
Some would argue that to make the model useful is to make the model less wrong, a very difficult task.
Some others would start by making an effort assessing whether the ``wrong'' model is useful, can ever be useful, or can be made useful without any direct improvement to the model.
The two views are not in contradictory, although the latter is arguably more humble.
This thesis is an effort in line with the latter view.

% Second part of the introductory paragraph
By many measures, \gls[hyper=false]{th} system codes for simulating coolant system behavior of a \gls[hyper=false]{npp} are an achievement.
Their development, by the best and the brightest, includes decades of verification and validation activities supported by numerous experimental facilities, small and large scales.
Many of the current understanding of physical phenomena in \gls[hyper=false]{npp} transient are established during that period.
Yet, their prediction can still be off when compared against experimental data.
The efforts to minimize this difference by developing high-fidelity physical models coupled with high-resolution numerical algorithms are always on-going and are indispensable moving forward.

% Third part of the introductory paragraph
At the same time, simulations are being continuously used to make decision, from optimal system design to safety margin evaluation for reactor licensing, 
As such, it is important to acknowledge the uncertainties associated with the predictions for robust decision-making on the basis of the predictions. 
Thus, independently to the efforts of improving the code, uncertainty quantification of the codes is an important part of the codes applications; it is the main topic of this thesis.

% Overview of the chapter
This opening chapter intends to introduce briefly the importance, the use and the challenges of using system code for simulating \gls[hyper=false]{th} behavior of \gls[hyper=false]{npp} in the context of its safety analysis.
Section~\ref{sec:intro_computer_simulation} starts with basic definitions of relevant terms used throughout the thesis before moving on to a brief introduction to safety analysis and thermal-hydraulics system code.
Uncertainty analysis of \gls[hyper=false]{th} system code is first discussed in Section~\ref{sec:intro_uncertainty_quantification}, outlining the background and the context of the doctoral research.

% Objectives, Scope, and Statistical Framework
Section~\ref{sec:intro_objectives_and_scope} then describes the statement of the problem, the objectives, and the scope of the research.
This thesis proposed a methodology comprises of sequential steps to analyze a computer model (i.e., \gls[hyper=false]{th} system code) with the overall goal of quantifying the uncertainty associated with the model parameters based on experimental data.
It consolidates and adapts recent developments of in the applied statistics literature.
In relation to that, Section~\ref{sec:intro_statistical_framework} provides a broad, rather biased and by no means exhaustive, overview of the research landscape on each of the proposed steps.
Finally, Section~\ref{sec:intro_thesis_structure} concludes the chapter by outlining the structure of the thesis.

% The contents of the chapter
\input{Chapters/1_introduction/computer_simulation}
\input{Chapters/1_introduction/uncertainty_quantification}
\input{Chapters/1_introduction/research_objectives}
\input{Chapters/1_introduction/statistical_framework}
\input{Chapters/1_introduction/thesis_structure}