\section{Gaussian Process Fundamentals}\label{sec:gp_fundamentals}

\subsection[Multivariate Normal Random Variable]{Multivariate Gaussian (Normal) Random Variable}\label{sub:gp_mvn}

Multivariate Normal (or Gaussian and hereinafter, \textsc{MVN}) random variabl is the most widely studied and applied random variable.
There are several reasons for this.
From a practical point of view, the distribution of MVN is tractable and is special properties are well known (citation needed).
From an epistemological point of view, as MVN distribution is fully characterized by its mean and covariance, only these wo parameters are of interest.
Furthermore, any dependence withing structure within a set of data can sufficiently be described linearly through the notion of statistical covariance.

This section reviews the definition and some of the most important properties of MVN random variable relevant in the present study.
In the next section, the MVN random variable is generalized to be defined on infinite-dimensional space through the notion of Gaussian stochastic process.

A collection of $D$ random variables $\mathbf{X} = [X_1, X_2, ...,X_D] \in \mathbb{R}^D$ is said to have a multivariate normal distribution with mean vector $\boldsymbol{\mu} \in \mathbb{R}^D$ and variance-covariance matrix $\boldsymbol{\Sigma} \in S_{++}^D$ if its joint probability density function is given by,

\begin{equation}
p(\mathbf{x};\boldsymbol{\mu},\boldsymbol{\Sigma}) = \frac{1}{2\pi^{D/2}|\boldsymbol{\Sigma}|^{1/2}} \exp{\left[-\frac{1}{2}(\boldsymbol{x}-\boldsymbol{\mu})^T\boldsymbol{\Sigma}^{-1}(\boldsymbol{x}-\boldsymbol{\mu})\right]}
\end{equation}

The joint distribution of MVN random variable is parameterized and fully specified by the mean vector $\boldsymbol{\mu}$ and the variance-covariance matrix $\boldsymbol{\Sigma}$. The symbol ``;'' separetes the value of the variates $\boldsymbol{x}$ from the parameters of the distribution. 
A $D$-variate random variable $\boldsymbol{X}$ distributed as multivariate normal is written as,

\begin{equation}
	\boldsymbol{X} \sim \mathcal{N}_D\left(\boldsymbol{\mu}, \boldsymbol{\Sigma}\right)
\end{equation}

where $\mathbb{E}$ is the expectation operator.

The variance-covariance matrix $\boldsymbol{\Sigma}$ is an element in the space of symmetric positive definite (PSD) $D \times D, S_{++}^D$ defined as,

\begin{equation}
	S_{++}^D = \{A \in \mathbb{R}^{D\times D}: A = A^T and \mathbf{x}^T A \mathbf{x} \geq 0, \forall \mathbf{x} \in \mathbb{R}^D \textnormal{and } \mathbf{x} \neq 0 \} 
\end{equation}

\subsection{Gaussian Process}


