%*******************************************************
% Acknowledgments
%*******************************************************
\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

% Opening Paragraph
This doctoral research has been conducted in the framework of the \glsentryshort{stars} project in the Laboratory for Reactor Physics and Systems Behavior (LRS)\footnote{which by the time this thesis is printed ceases to exist, but perhaps just metamorphosize to a better form...} at the \glsfirst[hyper=false]{psi}.
Although most of the funding was provided by the sister's laboratory of the same name at the Swiss Federal Institute of Technology, Lausanne (EPFL), the work was mainly carried out at \gls[hyper=false]{psi}.
Besides providing me with a comfortable working place, \glsentryshort{psi} through the \glsentryshort{stars} project also kindly financed all the trips taken during the course of the doctoral research, including NUTHOS-10 in Okinawa, NURETH-16 in Chicago, SAMO 2016 in Capri, NUTHOS-11 in Gyeongju, as well as several trips to the OECD/NEA office in Paris.

It is my cultural reflex to readily admit that any successful work is a collective effort, sometimes with God's blessing thrown into the mix;
while any eventual shortage is to be credited to me and me alone.
This is especially true for this work which at times -- if not most of the times -- felt really difficult to carry out.
So I am truly grateful for the support and contributions of so many people such that this work can be completed:
\begin{itemize}
	\item Prof. Andreas Pautz, the thesis director, for giving me the opportunity to conduct this research and to extend, again and again, my stay in Switzerland.
	I appreciate his support all these years and wish him all the best navigating the Nuclear Energy and Safety Division of \gls[hyper=false]{psi} in an evermore turbulent times.
	
	\item Mr. Omar Zerkak and Dr. Gregory Perret who have invested in me so much of their time, knowledge, and patience that allowed me to start and finish the thesis.
	I am truly grateful for those, especially when the thesis was becoming harder and harder to finish and I was on the verge of failing.
	
	\item Mr. Philippe Jacquemoud, in his own word an IT ``all-rounder'', who has been truly helpful providing me with IT related supports, but perhaps much more importantly, by being a very good friend.
  
	\item Dr. Jean Baccou, Prof. Bruno Sudret, and Dr. Winfried Zwermann for their willingness to sit on my PhD committee, evaluating the thesis over the Christmas holiday period and attending the defense.
  It has been my privilege to have them in my committee and I am truly grateful for their invaluable comments, feedback, and questions.
	
	\item Dr. Mathieu Hursin and Dr. Dimitri Rochman, who appeared to be genuinely interested in my work and gave invaluable comments during these period.
	
	\item Mr. Hakim Ferroukhi and Dr. Ivor Clifford who have always been appreciative and supportive towards my work in his laboratory and research group, respectively.
	
	\item Mrs. Ruth Ringele and Mrs. Andrea Mohr who have been truly kind and helpful dealing with my administrative matters during my PhD research.
  
	\item The present and past members of the \glsentryshort{lrs}, especially the \glsentryshort{stars} Coffee Club members who have created for me a conducive -- fun and most of the times productive -- working environment.
	
	\item Abhishek Saxena, Rita Szijártó, Yaroslav Sych, Olivier Leray, Carl Adamsson, Younsuk Yun, Raoul Happy-Ngayam, Gregory\footnote{déjà vu?} and Rebecca Lordan-Perret, Riccardo Puragliesi, Kinga Bernatowicz-Goma, Dionysios and Vera Chionis, Petra Mala, Vladimir Brankov, and Matthew and Deborah Stark-Studer; friends, some are newer than the others, but good friends all the same.
  It is easy to forget that I am thousands of kilometers away from home; during this period, these people have been -- in one way or another -- my ``immediate family''.
  \item Fauziah Satriana who provide me with a sense of being at home anywhere I am with her. Her patience and understanding towards me during the thesis write-up period will remain a mystery I am not willing to rationalize.
  \item My family back home: brothers, grandmother, sisters, aunts, and cousins who seem to be genuinely proud of what I have achieved.
\end{itemize}

\bigskip
\hspace*{0mm}-- WD41
